Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-17 RET_Hosts.tex
Updates from Overleaf

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES. The orange histogram represents the 97/106 DES RETs for which a host was detected. The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
\label{fig:sfms_sfr}}
\end{figure}

@@

We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey. This number expands upon the 72 of \citetalias{Pursiainen2018} and is presented in a companion work \citetalias{Pursiainen2020}. We refer to the full sample as DES RETs. In order to calculate host galaxy properties Of the 106 objects in the sample, \textbf{n} have a host galaxy detected in deep host galaxy photometry (Section \ref{sec:obs}), of which 49 have a host galaxy spectroscopic redshift. A further two have redshifts

>>>>

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/mag_dist.png}
\caption{Observer-frame $r$-band magnitude distribution for the host galaxies of RETs in DES. The orange histogram represents the 97/106 DES RETs for which a host was detected. The green histogram shows those that did not have a successful redshift measurement, while blue shows those with no redshift despite being targetted by OzDES.
\label{fig:mag_dist}}
\end{figure}

\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/z_dist.png}
\caption{Redshift distribution for the host galaxies of RETs in DES for which a measurement was obtained.
\label{fig:z_dist}}
\end{figure}

@@

We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey. This number expands upon the 72 of \citetalias{Pursiainen2018}. and is presented in a companion work \citetalias{Pursiainen2020}. We refer to the full sample as DES RETs. In order to calculate host galaxy properties Of the 106 objects in the sample, \textbf{n} have a host galaxy detected in deep host galaxy photometry (Section \ref{sec:obs}), of which 49 have a host galaxy spectroscopic redshift. A further three have redshifts obtained from narrow lines observed in spectra of the transients themselves. We do not consider these three objects for the analysis, since we are unable to separate transient and host contributions to the spectra.
